Supporting Information : Effect of copula on extinction risk

### 2019-02-25 SuppMat.Rmd
verhulst scl=3 changed from 2.5 to ensure 20-80% extinction risk range
minor plot edit

model<-"verhulst"
scl<-2.5

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=2.5) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_verhulst_r_vary_scl_2.5}](./Results/verhulst_scl_2.5/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=2.5) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_verhulst_r_vary_scl_2.5}](./Results/verhulst_scl_2.5/verhulst_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model with no dispersion : rc = 1, scl=2.5); numlocs=5, numsteps=25, numsims=10000\label{fig_verhulst_risk_d0_scl_2.5}](./Results/verhulst_scl_2.5/verhulst_extrisk_d0.pdf){ width=40%, height=40% }

>>>>

model<-"verhulst"
scl<-3

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=3) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_verhulst_r_vary_scl_2.5}](./Results/verhulst_scl_3/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=3) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_verhulst_r_vary_scl_2.5}](./Results/verhulst_scl_3/verhulst_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model with no dispersion : rc = 1, scl=3); numlocs=5, numsteps=25, numsims=10000\label{fig_verhulst_risk_d0_scl_2.5}](./Results/verhulst_scl_3/verhulst_extrisk_d0.pdf){ width=40%, height=40% }
